Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-27 manuscript/main.tex
revisions to paper

\externaldocument{tables/ideology_regressions.tex}
\externaldocument{tables/ncsl_crosstab.tex}
\externaldocument{tables/time_diff_reg.tex}

@@

There are a variety of algorithms designed to automatically detect text reuse between documents mostly originating in the plagiarism detection literature \citep[see e.g.][for an overview]{potthast2013overview}. In political science, \citet{wilkerson2015tracing} introduced the Smith-Waterman local alignment algorithm (SW algorithm) to detect overlapping language in congressional bills in order to trace policy ideas through the legislative process of the US Congress. We use the same algorithm to detect text reuse in US state bills, however, our implementation of the algorithm differs slightly. The SW algorithm was developed by \citet{smith1981identification} in molecular biology, in order to match genetic sequences. Given two sequences (of genes or words) it calculates the optimal alignment (match) between these sequences.

Sequences in text that convey similar---even equivalent---policy content often do not match perfectly. Formatting, white space, typographical errors, etc. would decrease the precision dramatically if only exact matches were used. The SW algorithm, therefore, returns the optimal alignment while allowing for mismatches and gaps. The extent to which such imperfections are tolerated is governed by parameters that are set by the researcher. There are three such parameters: the match score (reward for exactly matching words), the mismatch score (penalty for including words that do not match), and the gap score (penalty for including placeholder words in matching a shorter sequence to a longer sequence). The goal of the algorithm is to return the the alignment with the highest score given the input sequences and the parameters. Consider the following two excerpts from Alaska State Bill 203 (28th session) and North Carolina House Bill 366 (2015) respectively:

@@

There is a large number of possibilities of how these sequences could be aligned. There is a trade-off between short sequences that match perfectly, and longer sequences with imperfections. For example, we could match just ``is amended by adding new'' or ``compact for a balanced budget''. However, by adding a gap between ``adding'' and ``new'' in the first sequence and accepting the mismatches ``article''-``section'' and ``6.''-``80.'', a longer alignment can be obtained: ``is amended by adding \textit{(a)} new \textit{(article/section)} to read: article \textit{(6./80.)}''.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=1.05\textwidth]{figures/sm.png}
    \caption{Dynamic programming array of local alignment algorithm. The parameters in this instance are: Match Score: 5, Mismatch Score: -2, Gap Score: -1. The optimal alignment is displayed on the right side of the matrix. The left column corresponds to the text sequence in the rows of the matrix, the right column to the sequence in the columns. Mismatches are colored in red, gaps are indicated by "-" and orange color. The blue cells in the matrix display the path of the optimal alignment.}
    \label{fig:score_matrix}
\end{figure}

The four values of which the maximum is chosen in Equation \ref{eqn:fill}
describe four steps in this dynamic programming array. The first value
corresponds to a diagonal step which means in the resulting alignment sequence
elements $a_i$ and $b_j$ are matched and the score of the alignment is either
increased by $\delta$ if they match or decreased by $\epsilon$ if they don't
match. The second and third value describe a gap step either in horizontal or
vertical direction. That is, if we move from cell $(i,j)$ to cell $(i+1,j)$, in
the resulting alignment sequence element $a_{i+1}$ is matched with a gap. On the
other hand, if we move to cell $(i, j+1)$ sequence element $b_{j+1}$ is matched
with a gap in the resulting alignment. If the first three values are all $<= 0$,
the score in the cell is 0 meaning that no step is taken and every potential
alignment stops at this point. This can be observed in Figure \ref{fig:score_matrix}. The blue path describes the optimal alignment. The first two elements in both sequences don't match, therefore the score remains zero. Therefore the resulting alignment starts at the fourth element of each sequence with four diagonal steps, each adding points $(\delta = 5)$ to the final score which reaches 20 at the alignment ending in ``adding''-``adding''. After that, a step to the right is taken, meaning that the additional ``a'' in the column sequence is matched with a gap in the row sequence (indicated by ``-'' and orange coloring in the result on the right hand side). The cumulative score of the alignment is reduced by $\gamma = -1$ to 19. After that only diagonal steps are taken. Note that there are two mismatches each of which reduces the score by $\epsilon = -2$.

@@

The SW algorithm is computationally demanding and an exhaustive comparison of
all possible bill-pairs is not feasible (with $500,000$ bills this would amount
to about $124 * 10^9$ bill pairs). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with
similar language. We store all available bills in an Elastic Search database.
Elastic search is an open source web search engine which is designed to find
documents that match a search query \citep{gormley2015elasticsearch}. We utilize
the `more like this' query, which is designed to find documents that are similar
to a given document. It works in the following way: From the focus document, the
$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
search vector that is representative of the query document. Then, for each
document in the collection, a variation of the cosine similarity is calculated
and the $m$ bills with the highest scores are selected for further analysis. For
this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000\footnote{For
details on the exact algorithm we refer the reader to the elastic search
documentation (\url{http://sunlightfoundation.com/} as well as the lucene engine
documentation
(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
In order to account for the possibility of selection bias being introduced to
our analyses through the cap of 1000 similar bills, we analyzed the results with
different numbers of pre-selected bills. We find that this parameter, when set
to a sufficiently high value, does not lead to such bias because the set of
potentially relevant bills is always much smaller than 1000.}

@@

Once the candidate bills are selected, the alignments are calculated for all
possible bill-dyads, bill pairs from the same state are available but excluded
for the analyses below. We exclude same-state comparisons in the current analysis since our validation exercises are focused on cross-state comparisons. We refer to the two sections involved in each alignment process as `left' and `right' sections. The algorithm returns parts of the left and right section that are determined to be aligned as well as a score. We refer to these three pieces of information as an alignment.

@@

\begin{table}[ht!]
\centering
\caption{Alignment Examples. Yellow highlighting shows matching sections. Dashes stand for gaps introduced by the alignment algorithm. Non highlighted text are mismatches.}
\label{tab:alignment_examples}
\bgroup
\def\arraystretch{2}
\begin{tabular}{p{0.45\textwidth}|p{0.45\textwidth}|p{0.1\textwidth}}
Left Text & Right Text & Score\\
\hline

\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the} renewable energy property \hl{is placed in service but must be taken in five equal} - \hl{installments beginning with the taxable year in which the} renewable energy property \hl{is placed in service. if, in one of the years in which the installment of a credit accrues, the} renewable energy property \hl{with respect to which the credit was claimed is disposed of}, \hl{taken out of service, or moved out of state, the credit expires and the taxpayer may not take any remaining installment of the credit. the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & \textbf{nc\_2011\_SB747}: "\hl{the entire credit may not be taken for the taxable year in which the} facility - - \hl{is placed in service but must be taken in five equal} annual \hl{installments beginning with the taxable year in which the} facility - - \hl{is placed in service. if, in one of the years in which the installment of a credit accrues,} the facility - - \hl{with respect to which the credit was claimed is disposed} - - - \hl{of} - \hl{or taken out of service, the credit expires and the taxpayer may not take any remaining installment of the credit. the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & $388$ \\

\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the} taxable \hl{year in which the} renewable energy \hl{property is placed in service but must be taken in} five \hl{equal installments} - - - - - \hl{beginning with the taxable year in which the}" & \textbf{ga\_2011\_12\_HB146}: "\hl{the entire credit may not be taken for the} - \hl{year in which the} - - \hl{property is placed in service but must be taken in} four \hl{equal installments} over four successive taxable years \hl{beginning with the taxable year in which the}" & 110 \\

\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the}" renewable energy property is placed in service \hl{but must be taken in five equal installments beginning with the taxable year in which the} & \textbf{nc\_2009\_SB305}: "\hl{the entire credit may not be taken for the taxable year in which the} costs are paid - - - - \hl{but must be taken in five equal installments beginning with the taxable year in which the}" & 108\\
\hline
\end{tabular}
\egroup
\end{table}

@@

From this procedure we obtain ca. $1.2 * 10^8$ individual alignments (that is, shared
text between two bills). Figure \ref{fig:alignment_score_distribution} displays the cumulative frequency
distribution of the alignments. The vast majority of alignments are very small
(less than 50). Table \ref{tab:alignment_examples} displays three examples of alignments. The `Left Text' and `Right Text' columns display the optimal alignment for the two sections the alignment score is displayed in the `Score' column. This example shows the reuse of legislative text in three states (New Jersey, North Carolina and Georgia).

@@

The first approach also relies on an automatic classifier, but we propose a novel approach for
generating training data without relying on human coders. We posit that boiler plate language is highly repetitive within states. Furthermore, language
that is passed several times (i.e., in separate bills) within the same state is likely to be
substantively irrelevant. Using these facts allows us to accumulate a large amount of labeled data---all alignments between bills that have both passed in the same state---which we use to train a machine learning classifier to exclude boiler plate alignments. In addition to the text
itself, we use the position in the text as a feature in the classifier. This approach is very similar to that taken by \citet{wilkerson2015tracing}, except we would not use human coders to label boiler plate alignments.

In the second approach we describe, which we have implemented in the analyses we present below, we do not exclude boiler plate according to a classification dichotomy.
Rather, we down-weight alignments that consist of language that is
very common to all alignments. The underlying logic is that language that
appears in a large number of other alignments is probably not related to
specific policies. For example, alignments consisting of many stop words such as
`the' or `a' or of common procedural language like `legislature` or `section'
are most likely part of phrases that are either very frequent in common language
or very frequent in the legislative context. 
In order to quantify the similarity to common alignments, we calculate the
cosine similarity of the bag-of-words vector of each alignment with a random
sample of 1000 alignments\footnote{We rely on a random sample for computational
reasons. Calculating the complete similarity matrix is computationally
infeasible and unnecessary.}. The adjusted score for two bills $Y$ and $Y$ is
then:

@@

Where $S_{X,Y}$ is the alignment score as described in Section \ref{sec:d_t_r},
$\mathbf{\mathcal{A}_j}$ is the bag-of-word vector representation of the
matching alignment text and $i = 1,\dots,1000$ are the sample alignments.

@@

\begin{enumerate}
    \item Collect all urls returned by the web search query: ''site:ncsl.org ''legislation.aspx````\footnote{We used the bing websearch API to collect the urls.}
    \item Sample 50 urls
    \item Select bills that fulfill these three conditions:
        \begin{enumerate}
            \item The website is a NCSL table
            \item The table refers (at least in part) to legislation introduced in 2011 or later.          
             \item The table contains less than 100 individual bills. 
        \end{enumerate}
    \item Scrape all bills from these tables
\end{enumerate}

@@

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to avoid tables that cover very broad topics. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22
fulfilled the three criteria. From these 22 tables we constructed a dataset of
950 bills, of which we could match 704 to our bill database\footnote{We
    additionally excluded one bill. Indiana 2012 HB1009
    (\url{www.in.gov/legislative/bills/2012/HE/HE1009.1.html}), which is a
    very long bill containing technical corrections to a large number of
    other bills. Due to this fact it contains a large number of sections that
produce a large outlier alignment when aggregated}. Since this is a
relatively low number of bills, we then calculate the complete set of pairwise
alignments for these bills. As described above, we split the
bills in sections, calculate the pairwise section alignments. This results in
approximately $10^7$ section-dyads. We then aggregate these section-dyads to the
bill-dyad level.

Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
in predicting if two bills are in the same NCSL table. We present
precision---the proportion of bill pairs with a given alignment score that
exceed the threshold on the $x$-axis that are in the same NCSL table, and
recall---the proportion of same-NCSL-table pairs that exceed a given alignment
score threshold. We see very high precision when setting the threshold to
relatively high scores ($>100$). Recall is low at thresholds that produce
reasonable precision (above 100), but that is expected for our case, as
(1) the introduction of similar policies in bills in tow different states is a
rare event, and relatedly, (2) the appearance of two bills in the same NCSL
table is a relatively rare event (8\% in the current analysis); and classifier
recall is notoriously low in rare event data \citep{weiss2000learning}---even
commonly approaching zero, as in our case \citep{weiss2004mining}. Our results
suggest that the presence of a large alignment score between bills is an
effective indicator of policy similarity. {\bf FRIDO, I DON"T SEE ANYTHING ABOUT THE ADDITIONAL COMPARISONS YOU HAVE DONE HERE. WE DON'T REALLY PROVIDE THE READER WITH A BASELINE FOR COMPARISON HERE. WOULD YOU CALCULATE THE AUCPR OF OUR CLASSIFIER VS A RANDOM CLASSIFIER USING THE PRROC R PACKAGE? ALSO ADD THE VALUE USING THE COSINE SIMILARITY}

@@

@@

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Wed Sep 21 20:12:14 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
   & Coefficient & p-value & Coefficient & p-value \\  \hline
Intercept & -33577305.967 & 0.997 & 10.041 & 0.000 \\ 
  Diffusion Tie & 2423709.311 & 0.042 & 0.266 & 0.050 \\ 
    Coverage & 10938819.897 & 0.000 & 1.379 & 0.000 \\ 
\hline
\end{tabular}
\caption{Predicting aggregate cross-state alignment scores with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}

Results of the dyadic regression are presented in Table \ref{tab:qap.diffusion}. In both specifications there is a positive relationship between the number of diffusion ties and the number of alignments. The relationship is statistically significant at the 0.05 level (one tailed) in each analysis. Furthermore, the magnitudes of the relationships are substantively significant. With the identity link, the presence of a diffusion tie leads to a 0.25 standard deviation increase in the expected aggregate alignment score {\bf FRIDO, WOULD YOU VERIFY THE SD NUMBER HERE, OR EVEN JUST STANDARDIZE THE COEFFICIENTS IN THE IDENTITY LINK MODEL BY DIVIDING BY THE SD?}. Based on the log link, the addition of a diffusion tie corresponds to a 30\% increase in the expected aggregated alignment score.\footnote{Calculated as $100\times \left[ \exp(0.266)-1\right] = 30.47$}. These results offer further evidence of the validity of quantifying text re-use as a measure of policy similarity, as the aggregate volume of text re-use between states is positively associated with previously-identified diffusion ties between states.

>>>>

\externaldocument{tables/ncsl_auc.tex}

@@

There are a variety of algorithms designed to automatically detect text reuse
between documents mostly originating in the plagiarism detection literature
\citep[see e.g.][for an overview]{potthast2013overview}. In political science,
\citet{wilkerson2015tracing} introduced the Smith-Waterman local alignment
algorithm (SW algorithm) to detect overlapping language in congressional bills
in order to trace policy ideas through the legislative process of the US
Congress. We use the same algorithm to detect text reuse in US state bills,
however, our implementation of the algorithm differs slightly. The SW algorithm
was developed by \citet{smith1981identification} in molecular biology, in order
to match genetic sequences. Given two sequences (of genes or words) it
calculates the optimal local alignment (match) between these sequences.

Sequences in text that convey similar---even equivalent---policy content often
do not match perfectly. Formatting, white space, typographical errors, etc.
would decrease the recall dramatically if only exact matches were used. The SW
algorithm, therefore, returns the optimal alignment while allowing for
mismatches and gaps. The extent to which such imperfections are tolerated is
governed by parameters that are set by the researcher. There are three such
parameters: the match score (reward for exactly matching words), the mismatch
score (penalty for including words that do not match), and the gap score
(penalty for including placeholder words in matching a shorter sequence to a
longer sequence). The goal of the algorithm is to return the alignment with the highest score given the input sequences and the parameters. Consider the following two excerpts from Alaska State Bill 203 (28th session) and North Carolina House Bill 366 (2015) respectively:

@@

These sequences could be aligned in a large number of possible ways. There is a trade-off between short sequences that match perfectly, and longer sequences with imperfections. For example, we could match just ``is amended by adding new'' or ``compact for a balanced budget''. However, by adding a gap between ``adding'' and ``new'' in the first sequence and accepting the mismatches ``article''-``section'' and ``6.''-``80.'', a longer alignment can be obtained: ``is amended by adding \textit{(a)} new \textit{(article/section)} to read: article \textit{(6./80.)}''.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=1.05\textwidth]{figures/sm.png}
    \caption{Dynamic programming array of local alignment algorithm. The
    parameters in this instance are: Match Score: 5, Mismatch Score: -2, Gap
Score: -1. The optimal alignment is displayed on the right side of the matrix.
The left column corresponds to the text sequence in the rows of the matrix, the
right column to the sequence in the columns. Mismatches are colored in red, gaps
are indicated by "-" and orange color. The highlighted (blue) cells in the matrix display the path of the optimal alignment.}
    \label{fig:score_matrix}
\end{figure}

The four values of which the maximum is chosen in Equation \ref{eqn:fill}
describe four steps in this dynamic programming array. The first value
corresponds to a diagonal step which means in the resulting alignment sequence
elements $a_i$ and $b_j$ are matched and the score of the alignment is either
increased by $\delta$ if they match or decreased by $\epsilon$ if they don't
match. The second and third value describe a gap step either in horizontal or
vertical direction. That is, if we move from cell $(i,j)$ to cell $(i+1,j)$, in
the resulting alignment sequence element $a_{i+1}$ is matched with a gap. On the
other hand, if we move to cell $(i, j+1)$ sequence element $b_{j+1}$ is matched
with a gap in the resulting alignment. If the first three values are all $<= 0$,
the score in the cell is 0 meaning that no step is taken and every potential
alignment stops at this point. This can be observed in Figure
\ref{fig:score_matrix}. The highlighted (blue) path describes the optimal alignment. The first two elements in both sequences don't match, therefore the score remains zero. Therefore the resulting alignment starts at the fourth element of each sequence with four diagonal steps, each adding points $(\delta = 5)$ to the final score which reaches 20 at the alignment ending in ``adding''-``adding''. After that, a step to the right is taken, meaning that the additional ``a'' in the column sequence is matched with a gap in the row sequence (indicated by ``-'' and orange coloring in the result on the right hand side). The cumulative score of the alignment is reduced by $\gamma = -1$ to 19. After that only diagonal steps are taken. Note that there are two mismatches each of which reduces the score by $\epsilon = -2$.

@@

The SW algorithm is computationally demanding and an exhaustive comparison of
all possible bill-pairs is not feasible (with $500,000$ bills this would amount
to about $1.24 * 10^11$ bill pairs). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with
similar language. We store all available bills in an Elastic Search database.
Elastic search is an open source web search engine which is designed to find
documents that match a search query \citep{gormley2015elasticsearch}. We utilize
the `more like this' query, which is designed to find documents that are similar
to a given document. It works in the following way: From the focus document, the
$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
search vector that is representative of the query document. Then, for each
document in the collection, a variation of the cosine similarity is calculated
and the $m$ bills with the highest scores are selected for further analysis. For
this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000\footnote{For
details on the exact algorithm we refer the reader to the elastic search
documentation
(\url{https://www.elastic.co/guide/en/elasticsearch/reference/current/query-dsl-mlt-query.html} as well as the lucene engine
documentation
(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
In order to account for the possibility of selection bias being introduced to
our analyses through the cap of 1000 similar bills, we analyzed the results with
different numbers of pre-selected bills. We find that this parameter, when set
to a sufficiently high value, does not lead to such bias because the set of
potentially relevant bills is always much smaller than 1000.}.

@@

Once the candidate bills are selected, the alignments are calculated for all
possible bill-dyads. Bill pairs from the same state are available but excluded
for the analyses below. We exclude same-state comparisons in the current
analysis since our validation exercises are focused on cross-state comparisons.
We refer to the two bills involved in each alignment process as `left' and
`right' bills. The algorithm returns parts of the left and right bills that are determined to be aligned as well as a score. We refer to these three pieces of information as an alignment.

@@

%\begin{table}[ht!]
%\centering
%\caption{Alignment Examples. Yellow highlighting shows matching sections. Dashes stand for gaps introduced by the alignment algorithm. Non highlighted text are mismatches.}
%\label{tab:alignment_examples}
%\bgroup
%\def\arraystretch{2}
%\begin{tabular}{p{0.45\textwidth}|p{0.45\textwidth}|p{0.1\textwidth}}
%Left Text & Right Text & Score\\
%\hline
%\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the} renewable energy property \hl{is placed in service but must be taken in five equal} - \hl{installments beginning with the taxable year in which the} renewable energy property \hl{is placed in service. if, in one of the years in which the installment of a credit accrues, the} renewable energy property \hl{with respect to which the credit was claimed is disposed of}, \hl{taken out of service, or moved out of state, the credit expires and the taxpayer may not take any remaining installment of the credit. the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & \textbf{nc\_2011\_SB747}: "\hl{the entire credit may not be taken for the taxable year in which the} facility - - \hl{is placed in service but must be taken in five equal} annual \hl{installments beginning with the taxable year in which the} facility - - \hl{is placed in service. if, in one of the years in which the installment of a credit accrues,} the facility - - \hl{with respect to which the credit was claimed is disposed} - - - \hl{of} - \hl{or taken out of service, the credit expires and the taxpayer may not take any remaining installment of the credit. the taxpayer may, however, take the portion of an installment that accrued in a previous year and was carried forward to the extent permitted under}" & $388$ \\
%
%\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the} taxable \hl{year in which the} renewable energy \hl{property is placed in service but must be taken in} five \hl{equal installments} - - - - - \hl{beginning with the taxable year in which the}" & \textbf{ga\_2011\_12\_HB146}: "\hl{the entire credit may not be taken for the} - \hl{year in which the} - - \hl{property is placed in service but must be taken in} four \hl{equal installments} over four successive taxable years \hl{beginning with the taxable year in which the}" & 110 \\
%
%\textbf{nj\_214\_A1167}: "\hl{the entire credit may not be taken for the taxable year in which the}" renewable energy property is placed in service \hl{but must be taken in five equal installments beginning with the taxable year in which the} & \textbf{nc\_2009\_SB305}: "\hl{the entire credit may not be taken for the taxable year in which the} costs are paid - - - - \hl{but must be taken in five equal installments beginning with the taxable year in which the}" & 108\\
%\hline
%\end{tabular}
%\egroup
%\end{table}

\begin{table}[ht!]
\centering
\footnotesize
\caption{Alignment Examples. Bold (red) text are mismatches. Dashes (orange,
light text) are  gaps introduced by the alignment algorithm. Non highlighted
text are matches.}
\label{tab:alignment_examples}
\bgroup
\def\arraystretch{2}
\begin{tabular}{p{0.45\textwidth}|p{0.45\textwidth}|p{0.1\textwidth}}
Left Text & Right Text & Score\\
\hline
\textbf{nj\_214\_A1167}: ``the entire credit may not be taken for the taxable
year in which the \textcolor{red}{\textbf{renewable}} \textcolor{orange}{energy
property} is placed in service but must be taken in five equal
\textcolor{orange}{-} installments beginning with the taxable year in which the
\textcolor{red}{\textbf{renewable}} \textcolor{orange}{energy property} is
placed in service. if, in one of the years in which the installment of a credit
accrues, the \textcolor{red}{\textbf{renewable}} \textcolor{orange}{energy
property} with respect to which the credit was claimed is disposed
\textcolor{orange}{of, taken out} of \textcolor{orange}{service}, or
\textcolor{red}{\textbf{moved}} out of \textcolor{red}{\textbf{state,}} the
credit expires and the taxpayer may not take any remaining installment of the
credit. the taxpayer may, however, take the portion of an installment that
accrued in a previous year and was carried forward to the extent permitted
under'' & \textbf{nc\_2011\_SB747}: ''the entire credit may not be taken for the
taxable year in which the \textcolor{red}{\textbf{facility}}
\textcolor{orange}{- -} is placed in service but must be taken in five equal
\textcolor{orange}{annual} installments beginning with the taxable year in
which the \textcolor{red}{\textbf{facility}} \textcolor{orange}{- -} is placed
in service. if, in one of the years in which the installment of a credit
accrues, the \textcolor{red}{\textbf{facility}} \textcolor{orange}{- -} with
respect to which the credit was claimed is disposed \textcolor{orange}{- - -} of
\textcolor{orange}{-} or \textcolor{red}{\textbf{taken}} out of 
\textcolor{red}{\textbf{service,}} the credit expires and the
taxpayer may not take any remaining installment of the credit. the taxpayer may,
however, take the portion of an installment that accrued in a previous year and
was carried forward to the extent permitted under'' & $388$ \\

\textbf{nj\_214\_A1167}: ``the entire credit may not be taken for the
\textcolor{orange}{taxable} year in which the
\textcolor{orange}{renewable energy} property is placed in service but
must be taken in \textcolor{red}{\textbf{five}} equal installments
\textcolor{orange}{- - - - -} beginning with the taxable year in which the'' &
\textbf{ga\_2011\_12\_HB146}: ``the entire credit may not be taken for the
\textcolor{orange}{-} year in which the \textcolor{orange}{- -} property is
placed in service but must be taken in \textcolor{red}{\textbf{four}} equal
installments \textcolor{orange}{over four successive taxable years}
beginning with the taxable year in which the'' & 110 \\

\textbf{nj\_214\_A1167}: ``the entire credit may not be taken for the taxable
year in which the \textcolor{red}{\textbf{renewable energy property}}
\textcolor{orange}{is placed in
service} but must be taken in five equal installments beginning with the
taxable year in which the'' & \textbf{nc\_2009\_SB305}: ``the entire credit
may not be taken for the taxable year in which the \textcolor{red}{\textbf{costs
are paid}} \textcolor{orange}{- - - -}
but must be taken in five equal installments beginning with the taxable year
in which the'' & 108\\
\hline
\end{tabular}
\egroup
\end{table}

@@

 Table \ref{tab:alignment_examples} displays three examples of alignments. The `Left Text' and `Right Text' columns display the optimal alignment for the two sections the alignment score is displayed in the `Score' column. This example shows the reuse of legislative text in three states (New Jersey, North Carolina and Georgia).

For our data we obtain from this procedure ca. $1.2 * 10^8$ individual alignments (that is, shared
text between two bills). Figure \ref{fig:alignment_score_distribution} displays the cumulative frequency
distribution of the alignments. The lowest score is $2.3$, the highest $28811$ with a mean
alignment score of $18.8$ (median $14.9$). From this distribution it is clear that the
majority of alignments is small with only relatively few bill pairs having
large alignments. Of the $120$ million bill-pairs about $800,000$ have scores
larger than $100$ and ca. $44,000$ have scores larger than $1000$.

@@

The first approach also relies on an automatic classifier, but we propose a novel approach for
generating training data without relying on human coders. We posit that boiler plate language is highly repetitive within states. Furthermore, language
that is passed several times (i.e., in separate bills) within the same state is likely to be
substantively irrelevant. Using these facts allows us to accumulate a large
amount of labeled data---all alignments between bills that have both passed in
the same state---which could be used to train a machine learning classifier to exclude boiler plate alignments. In addition to the text
itself, the position in the text can be used as a feature in the classifier.
This approach is very similar to that taken by \citet{wilkerson2015tracing},
except that no human coders would be required to label boiler plate alignments.

In the second approach we describe, which we have implemented in the analyses we present below, we do not exclude boiler plate according to a classification dichotomy.
Rather, we down-weight alignments that consist of language that is
very common to all alignments. The underlying logic is that language that
appears in a large number of other alignments is probably not related to
specific policies. For example, alignments consisting of many stop words such as
`the' or `a' or of common procedural language like `legislature` or `section'
are most likely part of phrases that are either very frequent in common language
or very frequent in the legislative context. 
In order to quantify the similarity to common alignments, we calculate the
cosine similarity of the bag-of-words vector of each alignment with a random
sample of 1000 alignments\footnote{We rely on a random sample for computational
reasons. Calculating the complete similarity matrix is computationally
infeasible and unnecessary.}. The adjusted score for two bills $X$ and $Y$ is
then:

@@

Where $S_{X,Y}$ is the alignment score, calculated as described in Section \ref{sec:d_t_r},
$\mathbf{\mathcal{A}_i}$ is the bag-of-word vector representation of the
matching alignment text where $i = 1,\dots,1000$ are the sample alignments.

@@

\begin{enumerate}
    \item Collect all urls returned by the web search query: ''site:ncsl.org ''legislation.aspx````\footnote{We used the bing websearch API to collect the urls.}
    \item Sample 50 urls
    \item Select bills that fulfill the following three conditions:
        \begin{enumerate}
            \item The website is a NCSL table
            \item The table refers (at least in part) to legislation introduced in 2011 or later.          
             \item The table contains less than 100 individual bills. 
        \end{enumerate}
    \item Scrape all bills from these tables
\end{enumerate}

@@

Condition a) is necessary, since some of the urls returned by the web query refer to blog entries or to protected websites that require NCSL membership. The rationale behind condition b) is to maximize the number of bills we can match to our database (see Figure \ref{fig:bill_desc}). We additionally constrain the number of bills per table to be below 100, in order to avoid tables that cover very broad topics. We chose 100 since this number would correspond roughly to two bills per state (often there is a house and a senate bill in each state for a particular policy).
The web query from step 1 returned 266 urls. From the 50 sampled urls 22
fulfilled the three criteria. From these 22 tables we constructed a dataset of
950 bills, of which we could match 704 to our bill database. Since this is a
relatively low number of bills, we then calculate the complete set of pairwise
alignments for these bills. After removing same state bill pairs we obtained ca. $216,000$ alignments.

Figure \ref{fig:ncsl_prec_rec} displays the performance of the alignment score
in predicting if two bills are in the same NCSL table. We present
precision---the proportion of bill pairs with a given alignment score that
exceed the threshold on the $x$-axis that are in the same NCSL table, and
recall---the proportion of same-NCSL-table pairs that exceed a given alignment
score threshold. We see very high precision when setting the threshold to
relatively high scores ($>100$). Recall is low at thresholds that produce
reasonable precision (above 100), but that is expected for our case, as
(1) the introduction of similar policies in bills in tow different states is a
rare event, and relatedly, (2) the appearance of two bills in the same NCSL
table is a relatively rare event (8\% in the current analysis); classifier
recall is notoriously low in rare event data \citep{weiss2000learning}---even
commonly approaching zero, as in our case \citep{weiss2004mining}. Further more,
using a high precision - low recall classifier in our scenario where the total
number of bill pairs is extremely large, produces a large number of interesting
bill pairings in absolute terms.

\input{tables/ncsl_auc.tex}

For a better understanding how the alignment score classification performs in
comparison to other methods, in Table \ref{tab:ncsl_auc} we report the area under the ROC curve for the
alignment classifier compared to a classifier based on cosine similarity of bill
pairs and a random classifier. The first column contains the AUC values for each
classifier. The remaining two columns display bootstrapped one-tailed p-values for the
differences between the classifiers.Our results suggest that the presence of a large alignment score between bills is an effective indicator of policy similarity.

@@

%\begin{figure}[t!]
%    \centering
%    \begin{subfigure}[b]{0.5\textwidth}
%        \centering
%        \includegraphics[height=1.2in]{figures/ncsl_pr_nosplit.png}
%        \caption{Lorem ipsum}
%    \end{subfigure}%
%    ~ 
%    \begin{subfigure}[b]{0.5\textwidth}
%        \centering
%        \includegraphics[height=1.2in]{figures/ncsl_pr_cosim.png}
%        \caption{Lorem ipsum, lorem ipsum,Lorem ipsum, lorem ipsum,Lorem ipsum}
%    \end{subfigure}
%    \caption{Caption place holder}
%\end{figure}

@@

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Wed Sep 21 20:12:14 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
    & Coefficient & p-value & Coefficient & p-value \\
    Intercept & -3.297 & 0.997 & 9.014 & 0.000 \\ 
    Diffusion Tie & 0.238 & 0.042 & 0.239 & 0.050 \\ 
    Coverage & 1.074 & 0.000 & 1.238 & 0.000 \\ 
\hline
\end{tabular}
\caption{Predicting aggregate cross-state alignment scores with diffusion ties.
Coefficients calculated with OLS regression and normalized with standard
deviation of cross state alignment scores. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}

Results of the dyadic regression are presented in Table \ref{tab:qap.diffusion}. In both specifications there is a positive relationship between the number of diffusion ties and the number of alignments. The relationship is statistically significant at the 0.05 level (one tailed) in each analysis. Furthermore, the magnitudes of the relationships are substantively significant. With the identity link, the presence of a diffusion tie leads to a 0.23 standard deviation increase in the expected aggregate alignment score. Based on the log link, the addition of a diffusion tie corresponds to a 30\% increase in the expected aggregated alignment score.\footnote{Calculated as $100\times \left[ \exp(0.266)-1\right] = 30.47$}. These results offer further evidence of the validity of quantifying text re-use as a measure of policy similarity, as the aggregate volume of text re-use between states is positively associated with previously-identified diffusion ties between states.
